Pillar 1 - Sequential Pattern Mining

### 2019-02-14 Pillar 1 - Sequential Pattern Mining.Rmd

### Transcript with preceding courses (for SR by hand)
```{r d_transcript_cum}
#
# List of all courses
course_all <- unique(d_transactions$taken_PF_HL$item)

>>>>

### Transcript with preceding courses (for SR by hand)
For our analysis in sequential rule mining, we extract the history of each student, and create a transcript per student, per period, which contains information on the current courses, the courses taken before the current courses, courses taken so far (including current courses) and the courses not taken so far. 
```{r d_transcript_cum}
#
# List of all courses
course_all <- unique(d_transactions$taken_PF_HL$item)
